On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-06 Manuscript/manuscript.tex
Fixed Quotes and removed below

This CI is centered by the original point estimate $\hat\theta_n$ and is 
symmetric. The standard CI is classified by \citet{efron1993introduction} 
as a confidence interval based on bootstrap "tables". Its 
validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
approximated by its asymptotic normal distribution and whether the bootstrap
$\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI based on standard bootstrap is 
described in \citet{efron1993introduction}. Let $t_{(\alpha, k)}$ be the 
quantile function $F^{-1}(\alpha, k)$ of a $t$ distribution with $k$ degrees of 
freedom. With 
block bootstrapping, 
a $(1 - \alpha)100\%$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\widehat{\text{SE}}, \quad
\hat{\theta}_{n} - t_{(\alpha/2), k -1}\widehat{\text{SE}}),
\]
%\eds{define $t_{(.)}$ and check the signs}  \mc{addressed}
where $k$ is the number of blocks. This CI is centered by the original point 
estimate $\hat\theta_n$ and is symmetric. Like the standard normal interval, the
Student's $t$ CI is classified by \citet{efron1993introduction} 
as a confidence interval based on bootstrap "tables". In this case, its 
validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
approximated by the $t_{k-1}$ distribution with an expected value of $\theta$ 
and whether the bootstrap $\widehat{\text{SE}}$ approximates the true standard 
error.

@@

It is important to note that we expect the CIs that are based on bootstrap 
"tables" to depend on the 
asymptotic distribution of the statistics, but we expect such CIs to 
have similar performance for different error structures. For example, under the 
Central
Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
approximately 
normal for both marginal normal distributions and marginal exponential 
distributions. Therefore, we do not expect CIs that are not based on bootstrap
"tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better under
non-normal error structures.

@@

This study could be used as a guide for applied statistics courses for students
to generally understand how large of a sample size is sufficient for block
bootstrap to be used versus other inference methods. For undergraduate or 
graduate students, block bootstrap is not typically a part of curriculum, but
the results of this study can easily be used to demonstrate when it is practical 
to use this method. This information could also prove to be useful for research 
using block bootstrap estimation of time series in domains such as econometrics. 
Future studies could investigate the $n$ needed to make inferences about other 
forms of serially dependent data such as a moving average process. One could 
also investigate if there are types of block bootstrap interval construction 
such as $ABC$ or bootstrap-t intervals \citep{efron1993introduction} that could 
more
appropriately recover the parameters of a time series. We discussed some
drawbacks of block bootstrap in the introduction, which could motivate a similar
simulation study for alternatives to block bootstrap, such 
as AR-Sieve bootstrap, \citep{kreiss1992bootstrap} which 
\citet{buhlmann2002bootstraps} finds to be the best for linear time series. 
Lastly, because of its exceptional performance in comparison to the other 
CIs that are not based on bootstrap "tables", the proposed recentered percentile 
CI would be
an interesting method to study further with different bootstrap schemes.

>>>>

This CI is centered by the original point estimate $\hat\theta_n$ and is 
symmetric. The standard CI is classified by \citet{efron1993introduction} 
as a confidence interval based on bootstrap ``tables". Its 
validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
approximated by its asymptotic normal distribution and whether the bootstrap
$\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI based on standard bootstrap is 
described in \citet{efron1993introduction}. Let $t_{(\alpha, k)}$ be the 
quantile function $F^{-1}(\alpha, k)$ of a $t$ distribution with $k$ degrees of 
freedom. With 
block bootstrapping, 
a $(1 - \alpha)100\%$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\widehat{\text{SE}}, \quad
\hat{\theta}_{n} - t_{(\alpha/2), k -1}\widehat{\text{SE}}),
\]
%\eds{define $t_{(.)}$ and check the signs}  \mc{addressed}
where $k$ is the number of blocks. This CI is centered by the original point 
estimate $\hat\theta_n$ and is symmetric. Like the standard normal interval, the
Student's $t$ CI is classified by \citet{efron1993introduction} 
as a confidence interval based on bootstrap ``tables". In this case, its 
validity relies on whether the distribution of $\hat\theta_n$ is reasonably well 
approximated by the $t_{k-1}$ distribution with an expected value of $\theta$ 
and whether the bootstrap $\widehat{\text{SE}}$ approximates the true standard 
error.

@@

It is important to note that we expect the CIs that are based on bootstrap 
``tables" to depend on the 
asymptotic distribution of the statistics, but we expect such CIs to 
have similar performance for different error structures. For example, under the 
Central
Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
approximately 
normal for both marginal normal distributions and marginal exponential 
distributions. Therefore, we do not expect CIs that are not based on bootstrap
``tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better under
non-normal error structures.

@@

This study could be used as a guide for applied statistics courses for students
to generally understand how large of a sample size is sufficient for block
bootstrap to be used versus other inference methods. For undergraduate or 
graduate students, block bootstrap is not typically a part of curriculum, but
the results of this study can easily be used to demonstrate when it is practical 
to use this method. This information could also prove to be useful for research 
using block bootstrap estimation of time series in domains such as econometrics. 
Future studies could investigate the $n$ needed to make inferences about other 
forms of serially dependent data such as a moving average process. One could 
also investigate if there are types of block bootstrap interval construction 
such as $ABC$ or bootstrap-t intervals \citep{efron1993introduction} that could 
more
appropriately recover the parameters of a time series. We discussed some
drawbacks of block bootstrap in the introduction, which could motivate a similar
simulation study for alternatives to block bootstrap, such 
as AR-Sieve bootstrap, \citep{kreiss1992bootstrap} which 
\citet{buhlmann2002bootstraps} finds to be the best for linear time series. 
Lastly, because of its exceptional performance in comparison to the other 
CIs that are not based on bootstrap ``tables", the proposed recentered percentile 
CI would be
an interesting method to study further with different bootstrap schemes.

### 2024-01-06 Manuscript/reply.tex
Fixed Quotes and removed below

\jy{Left quote: `` (below the ESC key)}

@@

It is important to note that we expect the CIs that are based on bootstrap 
"tables" to depend on the 
asymptotic distribution of the statistics, but we expect such CIs to 
have similar performance for different error structures. For example, under the 
Central
Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
approximately 
normal for both marginal normal distributions and marginal exponential 
distributions. Therefore, we do not expect CIs that are not based on bootstrap
"tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better under
non-normal error structures.
\eds{you will need to add more here.  This concerns the
(asymptotic) distribution of the statistics, not the underlying error 
structure.}
\mc{I changed it a bit... I'm not sure what to say for circumstances in which
“non-parametric” CI 
formulas would work better}

@@

Thank you for the comment.  This terminology was used because 
\citet{efron1993introduction} refers to such CIs as 
"confidence intervals based on 
bootstrap 'tables'." We have changed these sentences as shown below:

The standard CI is classified by \citet{efron1993introduction} 
as a confidence interval based on bootstrap "tables".
Like the standard normal interval, the
Student's $t$ CI is classified by \citet{efron1993introduction} 
as a confidence interval based on bootstrap "tables".

@@

Lastly, because of its exceptional performance in comparison to the other 
CIs that are not based on bootstrap "tables", the proposed recentered percentile 
CI would be
an interesting method to study further with different bootstrap schemes.

@@

We modified the Design section as below:

@@

We have now repeated the same simulation study with block size as an 
additional experimental factor. The optimal order of block size is 
$\lceil n^{1/3} \rceil$, so we tried the same simulations using 
$l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$. We have included
the Appendix detailing these results below (the 
figures for 
$l = \lceil n^{1/3} \rceil$ are included for comparison):

>>>>

\jy{Left quote: `` (below the ESC key)}
\mc{addressed in reply and manuscript}

@@

It is important to note that we expect the CIs that are based on bootstrap 
``tables" to depend on the 
asymptotic distribution of the statistics, but we expect such CIs to 
have similar performance for different error structures. For example, under the 
Central
Limit Theorem, we expect the asymptotic distribution of the sample mean to be 
approximately 
normal for both marginal normal distributions and marginal exponential 
distributions. Therefore, we do not expect CIs that are not based on bootstrap
``tables" (Percentile, BC, BCA, Recentered Percentile CI) to perform better under
non-normal error structures.
\eds{you will need to add more here.  This concerns the
(asymptotic) distribution of the statistics, not the underlying error 
structure.}
\mc{I changed it a bit... I'm not sure what to say for circumstances in which
“non-parametric” CI 
formulas would work better}

@@

Thank you for the comment.  This terminology was used because 
\citet{efron1993introduction} refers to such CIs as 
``confidence intervals based on 
bootstrap `tables'." We have replaced all instances of the phrase 
``table-based bootstrap CIs" to ``confidence intervals based on bootstrap 
`tables'" for the sake of clarity.

%The standard CI is classified by \citet{efron1993introduction} 
%as a confidence interval based on bootstrap ``tables".
%Like the standard normal interval, the
%Student's $t$ CI is classified by \citet{efron1993introduction} 
%as a confidence interval based on bootstrap ``tables".

@@

Lastly, because of its exceptional performance in comparison to the other 
CIs that are not based on bootstrap ``tables", the proposed recentered percentile 
CI would be
an interesting method to study further with different bootstrap schemes.

@@

Thank you for pointing this out. We modified the Design section to include a 
specification of the interval type for the coverage rate:

@@

We have now repeated the same simulation study with block size as an 
additional experimental factor. The optimal order of block size is 
$\lceil n^{1/3} \rceil$, so we tried the same simulations using 
$l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$. We have included
an Appendix detailing these results:
